The Feasibility of Stylometry as a Service

### 2013-12-08 paper/paper.tex
Paper improvements for implementation and security

@@

@@

@@

\section{Privacy Analysis}

@@

@@

@@

>>>>

The performance of the Stylometry Service

@@

A number of attack vectors for the web application currently exist. We
discuss those which seem most significant here below. However one key
security implication of a web-delivered Stylometry Service is that it
is expected to be delivered over the web, can be accessed in this configuration by anyone with knowledge of its unique URL (or .onion
address). This allows adversaries greater opportunity to attempt to
penetrate the security of the web application relative to a client
application installed on a PC that is not internet connected.

It is expected that, before the service would be used in a real-world
use case, a user would configure and deploy supporting databases
associated with the login and SSL options available in the
Play Framework.

Although web accessbility may be a significant risk from a usability
standpoint, the anecdotal infrequency with which adversarial
stylometry software is used even among privacy-conscious users as
determined by conversations with colleagues of the authors
suggests that delivery of this functionality via a web page (or even
potentially via a browser plugin functional across multiple web pages)
may be an appropriate trade-off to make.

Beyond the concerns mentioned above, a number of specific attack
vectors remain for a stylometric web service in general and for our
implementation in particular:

Man in the middle attacks: If a user accepts a rogue SSL certificate, it
may be possible to create a "man in the middle" attack where the user
believes he/she is communicating with a specific Stylometry Service,
but is infact communicating via an impersonated target.

Replay attacks: An evesdropper may 'replay' a message to the
webservice in an attempt to surrepituously revert parts of the text to
earlier versions. This may be possible as it is not documented whether
the current implementation uses nonces when transmitting messages.

HTML5 Canvas attacks: The etherpad implementation uses the new
'canvas' element introduced in HTML5 extensively. Recently an attack
has been documented
(http://www.contextis.com/files/Browser_timing_Attacks.pdf) whereby
Firefox optimizations in the implementation of the
requestAnimationFrame method have been used by to detect differences
in link coloring across frames (allowing an adversary to determine if
a particular styometry service has been visited, for instance)

Note: We do not know if any of these vectors allows for a specific
attack, but suggest they should be considered for any future
implementation research in the area of stylometric web services using
a similar architecture.

@@

The web service UI is amenable to automated testing via web testing
frameworks such as Selenium (although such tests were not written for
this project). JUnit tests, in contrast, were written to test both
service method paths implemented. The authors consider the fact that
this application is delivered as a web application with a distinct
service layer to be a positive from the standpoint of testability, as
it allows users who may wish to modify the service the ability to
expand an existing unit test suite.

@@

\section{Privacy and Anonymity Analysis}

The privacy of a user accessing the web service is expected to be
ensured via the use of TLS/SSL encryption for all data transmitted
between the client and server. The anonymity of the user is expected
to be promoted via the use of an Onion Routing protocol such as Tor,
to ensure that the IP of the client cannot be directly linked to the
IP of the service.

@@

We implemented a web application based on the Play Web Application
Framework in Java. This web application had a reference to a modified
version of JSAN which was forked from the PSAL Anonymouth repository
(https://github.com/psal/anonymouth) on September 29, 2013. In
addition the application has major dependencies on JQuery, Twitter
Bootstrap (for page layout), and Etherpad  (an open-source collaborative text editing
web application and library). Etherpad (specifically Etherpad Lite is
the version used here) in turn has major dependencies on
node.js for building and running the backend service.

At a high level the implementation is as follows: A user browses to
the Stylometry Service via a web browser. This causes the Play
Framework web application to serve up a web page with an Etherpad control
and instructions for the user to enter in the document they wish to
anonymize. The etherpad control is implemented as an iframe which
serves an Etherpad that is connected to the node.js server running the
Etherpad backend (both servers should reside on the same domain,
running on different ports). The page served by Play also contains a
button which allows the author to specify when he or she would like to
submit the document for anonymization to Anonymouth. Because the
Anonymouth analysis process depends on a number of
computationally-intensive algorithms (among them running SMO analysis
in Weka as well as a Basic-9 feature stylometric analysis) we
implemented this calculation asynchronously. When a user clicks the
button to run an analysis, JQuery is used to issue a HTTP POST
containing in the message body a JSON-encoded
representation of the current Etherpad text to an endpoint at
/getAnonymouthInfoJSON. During the time that the Anonymouth analysis
is underway, a spinner control from the spin.js library is used to
indicate to the user than an analysis is underway. The fact that the
request is made to Anonymouth asynchronously allows a user to continue
editing the text while an analysis is running, allowing for a smooth
user experience.

The web service as implemented currently supports only 1 author as the assumption is
made that the author has pre-configured the "doc set" (also referred
to as 'problem set' in Anonymouth source) that provides references as
to the author's own writing style, as well as writing samples for
other authors that will be used as a reference for writing styles that
are different than that of the active author. The user can
additionally configure the anonymouth properties file
(anonymouthprop.prop) in the jsan resources directory to influence
settings such as the feature set to use for stylometric identification
as well as the number of threads to use and maximum number of features
to analyze.

One configured, the call to the getAnonymouthInfoJSON input will
overwrite the "test.txt" file on disk that is configured in the provided problem
set. This will ensure that changing the document in Etherpad forces an
update to the test file and thus ensuring that the 'latest' document
is always anonymized. Once the problem set has been updated, the
'Anonymouth library' is invoked. The 'Anonymouth library' is a forked
version of the current Anonymouth application, which is designed to be
used behind a Swing/AWT rich client GUI. A number of implementation
challenges were present when trying to separate the core anonymization
logic of Anonymouth from its GUI implementation - most specifically,
although an 'engine' namespace exists which holds much of the
anonymization logic, significant dependencies still existed between
the 'engine' and the 'GUI' namespaces, specifically in the event
handlers associated with the Editor screen and the GUIMain classes. Much of the work in this
project consisted of reducing the coupling between these two
namespaces.

As much of the configuration logic was handled at the GUI layer (via
ThePresident and GUIMain classes) we took the approach of refactoring
the GUI layer to work in a 'headless' mode, that is, without any
windows launching. Long-term it would be preferable to have no
dependencies on the GUI namespace at all for the Stylometry Service,
however this could not be achieved in the available timeframe for this
project. The web service thus invokes a modified version of the
ThePresident class, which coordinates reading configuration files,
loading the configured problem set, and using numerous libraries
(JGAAP and Weka among them) to conduct an adversarial stylometric
analysis. The results are returned by the web service in the form of a
JSON-encoded list of words to remove, as well as an indication of
'changes needed' to the current text to reach an acceptable level of
anonynmity.

While this analysis has been running, the UI has been waiting on a
response to the request made of the Stylometric Service. Once this
request is returned, a request is made to spin.js library to stop the
spinner, and JQuery is again used to update a div on the page with the
results of the adversarial stylometric analysis. The JQuery Promises
interface was used to ensure that the UI correctly waited for these
otherwise asynchronous requests to be completed in the right order.

The web application (bundled with all dependencies) can be downloaded
by cloning https://github.com/LRParser/anonymouth and running the
following command:

./bootstrap.sh

This command will copy the latest JSAN JAR files to the 'lib'
directory of the Play Framework Web Application, start a Play
Framework Server on port 9000, and start an Etherpad Lite server on
port 9001 over node.js.

@@

The stand-alone application has both advantages and disadvantages
relative to the web service. To start with advantages: it contains
more robust error handling, offers a GUI to create a problem set, and
provides a richer editing experience for anonymized
texts. Disadvantages concern ease of use (users must download and
execute a JAR file) and supported platforms (it is unlikely that this
JAR file will be supported on many mobile phones, for instance). The
Stylometry Service, in contrast, is potentially more accessible than
the standalone application: it can be accessed via mobile phones and
tablets, for instance. Likewise application delivery may be simpler -
nothing must be downloaded locally. Furthermore, the web application
maintains a 'timeline' of changes made to a text and also allows for
simple multi-party anonymization of documents.

Disadvantages to the web application include the fact that it offers fewer anonymization
features (for instance, highlighting of specific text passages),
instead focusing primarily on 'words to remove'. Furthermore, its
security footprint is less well known, as it introduces a number of
new dependencies / potential attack vectors such as JQuery, Twitter
Bootstrap, Etherpad Lite, node.js, etc.

For a user likely to be using
mobile devices or a casual user looking to quickly anonymize texts,
we suggest that the web interface may be a better option. For a user
facing a highly sophisticated adversary and needing detailed
anonymization suggestions, we suggest that the stand-alone application
may be a better option. We note that there is no technical reason that
could keep the web application from offering all of the same
anonymization suggestions as the standalone application, and thus is
may be the case that in the future the web application could be
recommendable to a wider range of users.
standalone client

@@

Although time didn't permit detailed user testing of the web
application, the authors did conduct one experiment with two users
using Amazon Mechanical Turk. Users were given 45 minutes to anonymize
a document. The title of the request was "Help re-phrase approx. 500
word texts as part of a research project". Specifically users were
asked, 'Re-phrase the text in the below-linked document while keeping
the original meeting. Substitute synonyms, change punctuation (I am to
I'm), split up / join sentences, etc. This is part of a research
project to see how well different persons can make a text appear as if
it wasn't written by the original author.'

The responses of users on Mechanical Turk (who were trying to
anonymize a text without any supporting software) were compared with
anonymization attempts by the authors of this paper against the same
document. The anonymization attempts by the authors took place before
reviewing the submissions from Mechanical Turk. For one sample paper,
d 09.txt from the Brennan-Greenstadt corpus (Michael Brennan and Rachel Greenstadt. Practical Attacks Against Authorship Recognition Techniques in Proceedings of the Twenty-First Conference on Innovative Applications of Artificial Intelligence (IAAI), Pasadena, California, July 2009.
), we noted that Anonymouth returned a "changes needed" score
on the original document of 2.518, 2.677 for the users 'naive' attempt
to anonymize over Mechanical Turk, and 2.467 for the attempt of one of
the authors to anonymize using the web application created in this
paper. Each of the two anonymization attempts for the 500-word
document took approximately 15 minutes. Although these results are far from achieving statistical
significance, they do suggest that it may be possible to use this
software to achieve anonymization levels which surpass those of a
'naive' anonymization attempt.
